---
title: "investigations"
author: "Paula Wu"
date: "5/11/2022"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(patchwork)
library(caret)
library(GGally)
library(nlme)
library(lme4)
library(stringr)
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
theme_set(theme_minimal() + theme(legend.position = "bottom") + theme(plot.title = element_text(hjust = 0.5)))
```

```{r}
m2_df = 
  read_csv("./data/m2_df.csv") %>% 
  select(-1) %>% 
  filter(B3TCOMPZ3 != 8 & B3TEMZ3 != 8 & B3TEFZ3 != 8) %>% 
  filter(B4QCT_SA != 98 & B4QCT_EN != 98 & B4QCT_MD != 8 & B4QCT_PN != 98 & B4QCT_EA != 98 & B4QCT_PA != 98)
```


## SES and Spouse SES Investigation
For now, I'm thinking about impute those missing numbers with their spouse's SES, if any. First, investigate: how many people have their spouse's SES filled (out of 352)
```{r}
m2_df %>% 
  filter(B1PTSEI == 999) %>% 
  select(M2ID, M2FAMNUM, B1PTSEI, B1PTSEIS) %>% 
  mutate(nul = ifelse(B1PTSEIS == 999, 1, 0)) %>% 
  group_by(nul) %>% 
  summarize(n = n())
```
Out of 352 missing, 129 of them still don't have the spouse SES while 223 of them did. 

### imputation - Jun 2nd (final) version:
Impute spouses' SES for those who doesn't have SES; for the rest use LM (education as predictor) for imputation

```{r}
# for those whose spouse has a valid SES
with_sps = 
  m2_df %>% 
  filter(B1PTSEI == 999) %>% 
  select(M2ID, M2FAMNUM, B1PTSEI, B1PTSEIS) %>% 
  filter(B1PTSEIS != 999) %>% 
  pull(M2ID)
m2_df[m2_df$M2ID %in% with_sps, which(colnames(m2_df) == "B1PTSEI")] = m2_df[m2_df$M2ID %in% with_sps, which(colnames(m2_df) == "B1PTSEIS")]

# for those whose spouse doesn't have a valid SES, fit an LM 
m2_df_lm = m2_df %>% 
  select(B1PTSEI, B1PAGE_M2, B1PB1) %>% 
  filter(B1PTSEI != 999 & B1PB1 != 97)
lm_ses = lm(B1PTSEI ~ B1PB1, data = m2_df_lm)

# prediction
m2_pred_id = m2_df %>% 
  filter(B1PTSEI == 999) %>% 
  pull(M2ID)

for (i in m2_pred_id){
  edu = m2_df[m2_df$M2ID == i, which(colnames(m2_df) == "B1PB1")]
  pred_ses = predict(lm_ses, newdata = edu)
  m2_df[m2_df$M2ID == i, which(colnames(m2_df) == "B1PTSEI")] = pred_ses
}
```

```{r}
m2_df_copy = m2_df
m2_df_invalid = 
  m2_df_copy %>% 
  mutate(B3TCOMPZ3_ = ifelse(B3TCOMPZ3 == 8, 1, 0),
         B3TEMZ3_ = ifelse(B3TEMZ3 == 8, 1, 0),
         B3TEFZ3_ = ifelse(B3TEFZ3 == 8, 1, 0),
         B4QCT_SA_ = ifelse(B4QCT_SA == 98, 1, 0),
         B4QCT_EN_ = ifelse(B4QCT_EN == 98, 1, 0),
         B4QCT_MD_ = ifelse(B4QCT_MD == 8, 1, 0),
         B4QCT_PN_ = ifelse(B4QCT_PN == 98, 1, 0),
         B4QCT_EA_ = ifelse(B4QCT_EA == 98, 1, 0),
         B4QCT_PA_ = ifelse(B4QCT_PA == 98, 1, 0),
         B1PTSEI_ = ifelse(B1PTSEI == 999, 1, 0),
         B4HMETMW_ = ifelse(B4HMETMW == 99998, 1, 0),
         B1PB1_ = ifelse(B1PB1 == 97, 1, 0),
         B1PF7A_ = ifelse(B1PF7A >= 7, 1, 0),
         B1SA62A_ = ifelse(B1SA62A == 8, 1, 0),
         B1SA62B_ = ifelse(B1SA62B == 8, 1, 0),
         B1SA62C_ = ifelse(B1SA62C == 8, 1, 0),
         B1SA62D_ = ifelse(B1SA62D == 8, 1, 0),
         B1SA62E_ = ifelse(B1SA62E == 8, 1, 0),
         B1SA62F_ = ifelse(B1SA62F == 8, 1, 0),
         B1SA62G_ = ifelse(B1SA62G == 8, 1, 0),
         B1SA62H_ = ifelse(B1SA62H == 8, 1, 0),
         B1SA62I_ = ifelse(B1SA62I == 8, 1, 0),
         B1SA62J_ = ifelse(B1SA62J == 8, 1, 0),
         B1SPWBA2_ = ifelse(B1SPWBA2 == 98, 1, 0),
         B1SPWBE2_ = ifelse(B1SPWBE2 == 98, 1, 0),
         B1SPWBG2_ = ifelse(B1SPWBG2 == 98, 1, 0),
         B1SPWBR2_ = ifelse(B1SPWBR2 == 98, 1, 0),
         B1SPWBU2_ = ifelse(B1SPWBU2 == 98, 1, 0),
         B1SPWBS2_ = ifelse(B1SPWBS2 == 98, 1, 0),
         B1SMASTE_ = ifelse(B1SMASTE == 8, 1, 0),
         B1SCONST_ = ifelse(B1SCONST == 8, 1, 0),
         B1SCTRL_ = ifelse(B1SCTRL == 8, 1, 0),
         B1SESTEE_ = ifelse(B1SESTEE == 98, 1, 0),
         B1SINTER_ = ifelse(B1SINTER == 8, 1, 0),
         BASINTER_ = ifelse(B1SINTER == 98, 1, 0),
         B1SINDEP_ = ifelse(B1SINDEP == 8, 1, 0),
         BASINDEP_ = ifelse(B1SINDEP == 98, 1, 0),
         B1SAGENC_ = ifelse(B1SAGENC == 8, 1, 0),
         B1SAGREE_ = ifelse(B1SAGREE == 8, 1, 0),
         B1SEXTRA_ = ifelse(B1SEXTRA == 8, 1, 0),
         B1SNEURO_ = ifelse(B1SNEURO == 8, 1, 0),
         B1SCONS1_ = ifelse(B1SCONS1 == 8, 1, 0),
         invalid_ind = NA) %>% 
  select(-c(2:60)) %>% 
  select(M2ID, invalid_ind, everything()) %>% 
  rename_at(.vars = vars(ends_with("_")),
            .funs = funs(sub("_$", "", .)))

invalid_var = function(obs){
  invalid_str = ""
  for (i in 3:44){
    cell = as.numeric(obs[i])
    if(cell == 1){
      invalid_str = paste0(invalid_str, colnames(obs)[i], sep = ", ")
    }
  }
  return(invalid_str)
}

for (i in 1:1099){
  obs = m2_df_invalid[i,]
  invalid_str = invalid_var(obs)
  m2_df_invalid[i,2] = invalid_str
}
invalid_full = 
  m2_df_invalid %>% 
  select(M2ID, invalid_ind) %>% 
  filter(!invalid_ind == "") %>% 
  mutate(invalid_count = str_count(invalid_ind, pattern = ","))

invalid_full %>% 
  group_by(invalid_count) %>% 
  summarize(n = n()) %>% 
  knitr::kable()

invalid_full %>% 
  ggplot(aes(x = invalid_count))+
  geom_histogram() +
  stat_bin(aes(y=..count.., label=ifelse(..count..== 0,"",..count..)), geom="text", vjust= -0.5)
```

```{r}
a = m2_df %>% 
  filter(!(B4QCT_EA == 98 | B4QCT_EN == 98 | B4QCT_SA == 98 | B4QCT_PA == 98 | B4QCT_PN == 98 | B4QCT_MD == 8 )) %>% 
  mutate(ctq_total = B4QCT_EA + B4QCT_EN + B4QCT_SA + B4QCT_PA + B4QCT_PN + B4QCT_MD)

mean_ctq = a %>% 
  pull(ctq_total) %>% 
  mean() %>% 
  signif(6)

median_ctq = a %>% 
  pull(ctq_total) %>% 
  median() %>% 
  signif(6)

a %>% 
  ggplot(aes(x = ctq_total)) +
  geom_density()+
  geom_vline(xintercept=mean_ctq, size=0.5, color="red")+
  geom_text(aes(x=mean_ctq + 5, label=paste0("Mean\n",mean_ctq), y=0.03), color = "red")+
  geom_vline(xintercept=median_ctq, size=0.5, color="blue")+
  geom_text(aes(x=median_ctq - 3, label=paste0("Median\n",median_ctq), y=0.03), color = "blue")+
  theme(legend.position = "none")+
  xlab("CTQ Total Score")+
  ylab("Density")

a %>% 
  mutate(below_49 = ifelse(ctq_total <= 39, 1, 0)) %>% 
  group_by(below_49) %>% 
  summarize(n = n())
#ggsave("ctq_density.jpeg", width = 10, height = 7)
```
## Invalid investigation, after imputation
```{r}
m2_df_cc = m2_df %>% 
  mutate(B3TCOMPZ3_ = ifelse(B3TCOMPZ3 == 8, 1, 0),
         B3TEMZ3_ = ifelse(B3TEMZ3 == 8, 1, 0),
         B3TEFZ3_ = ifelse(B3TEFZ3 == 8, 1, 0),
         B4QCT_SA_ = ifelse(B4QCT_SA == 98, 1, 0),
         B4QCT_EN_ = ifelse(B4QCT_EN == 98, 1, 0),
         B4QCT_MD_ = ifelse(B4QCT_MD == 8, 1, 0),
         B4QCT_PN_ = ifelse(B4QCT_PN == 98, 1, 0),
         B4QCT_EA_ = ifelse(B4QCT_EA == 98, 1, 0),
         B4QCT_PA_ = ifelse(B4QCT_PA == 98, 1, 0),
         B1PTSEI_ = ifelse(B1PTSEI == 999, 1, 0),
         B4HMETMW_ = ifelse(B4HMETMW == 99998, 1, 0),
         B1PB1_ = ifelse(B1PB1 == 97, 1, 0),
         B1PF7A_ = ifelse(B1PF7A >= 7, 1, 0),
         B1SA62A_ = ifelse(B1SA62A == 8, 1, 0),
         B1SA62B_ = ifelse(B1SA62B == 8, 1, 0),
         B1SA62C_ = ifelse(B1SA62C == 8, 1, 0),
         B1SA62D_ = ifelse(B1SA62D == 8, 1, 0),
         B1SA62E_ = ifelse(B1SA62E == 8, 1, 0),
         B1SA62F_ = ifelse(B1SA62F == 8, 1, 0),
         B1SA62G_ = ifelse(B1SA62G == 8, 1, 0),
         B1SA62H_ = ifelse(B1SA62H == 8, 1, 0),
         B1SA62I_ = ifelse(B1SA62I == 8, 1, 0),
         B1SA62J_ = ifelse(B1SA62J == 8, 1, 0),
         B1SPWBA2_ = ifelse(B1SPWBA2 == 98, 1, 0),
         B1SPWBE2_ = ifelse(B1SPWBE2 == 98, 1, 0),
         B1SPWBG2_ = ifelse(B1SPWBG2 == 98, 1, 0),
         B1SPWBR2_ = ifelse(B1SPWBR2 == 98, 1, 0),
         B1SPWBU2_ = ifelse(B1SPWBU2 == 98, 1, 0),
         B1SPWBS2_ = ifelse(B1SPWBS2 == 98, 1, 0),
         B1SMASTE_ = ifelse(B1SMASTE == 8, 1, 0),
         B1SCONST_ = ifelse(B1SCONST == 8, 1, 0),
         B1SCTRL_ = ifelse(B1SCTRL == 8, 1, 0),
         B1SESTEE_ = ifelse(B1SESTEE == 98, 1, 0),
         B1SINTER_ = ifelse(B1SINTER == 8, 1, 0),
         BASINTER_ = ifelse(B1SINTER == 98, 1, 0),
         B1SINDEP_ = ifelse(B1SINDEP == 8, 1, 0),
         BASINDEP_ = ifelse(B1SINDEP == 98, 1, 0),
         B1SAGENC_ = ifelse(B1SAGENC == 8, 1, 0),
         B1SAGREE_ = ifelse(B1SAGREE == 8, 1, 0),
         B1SEXTRA_ = ifelse(B1SEXTRA == 8, 1, 0),
         B1SNEURO_ = ifelse(B1SNEURO == 8, 1, 0),
         B1SCONS1_ = ifelse(B1SCONS1 == 8, 1, 0),
         invalid_ind = NA) %>% 
  select(-c(2:60)) %>% 
  select(M2ID, invalid_ind, everything()) %>% 
  rename_at(.vars = vars(ends_with("_")),
            .funs = funs(sub("_$", "", .)))
for (i in 1:1099){
  obs = m2_df_cc[i,]
  invalid_str = invalid_var(obs)
  m2_df_cc[i,2] = invalid_str
}
invalid_cc = 
  m2_df_cc %>% 
  select(M2ID, invalid_ind) %>% 
  filter(!invalid_ind == "") %>% 
  mutate(invalid_count = str_count(invalid_ind, pattern = ","))

# quick summary: invalid entries of each variable
colSums(m2_df_cc[3:44])

# quick summary: count of people for different numbers of invalid entries. Total: 40 subjects
invalid_cc %>% 
  group_by(invalid_count) %>% 
  summarize(n = n()) %>% 
  knitr::kable()
```

```{r}
m2_df = m2_df %>% 
  select(-c(B3PIDATE_MO, B3PIDATE_YR, B1PTSEIS, B1PA37, B1PA38A, B1SA11Z, B4H33, B4H34, B4H36, B4H38, B4H40))
```

# M3 dataframe
```{r}
m2_id = m2_df %>% pull(M2ID)

m3_df = 
  read_csv("./data/m3_df.csv") %>% 
  select(-1)

# only 930 left, the rest 169 don't have M3 record
full_df = 
  inner_join(m2_df, m3_df, by = "M2ID") %>% 
  select(-M2FAMNUM.y) %>% 
  rename(M2FAMNUM = M2FAMNUM.x) %>% 
  mutate(D3TCOMP = C3TCOMP - B3TCOMPZ3,
         D3TEM = C3TEM - B3TEMZ3,
         D3TEF = C3TEF - B3TEFZ3,
         D1PB19 = C1PB19 - B1PB19,
         B1PF7A = as.factor(B1PF7A))
```


# Modeling
right now I just completely filter out all the observations with at least one invalid feature, in total there are 40 of them, not a small number.


first, maybe the most primitive one, here are a list of covariates

* ctq total score (for now)
* age
* sex
* race
* (imputed) SES
* changes in marital status
* 


```{r}
invalid_cc_id = invalid_cc %>% 
  pull(M2ID) %>% 
  unique()

full_df_no_invalid = full_df %>% 
  mutate(ctq_total = B4QCT_EA + B4QCT_EN + B4QCT_SA + B4QCT_PA + B4QCT_PN + B4QCT_MD) %>% 
  filter(!(M2ID %in% invalid_cc_id))


lmm1 = lme(D3TEM ~ ctq_total + B1PAGE_M2 + B1PTSEI + B1PF7A + D1PB19, random = ~1 | M2FAMNUM, data = full_df_no_invalid) 
summary(lmm1)

```


# PCA of the modifiers

...

