---
title: "File I/O"
author: "Paula Wu"
date: "4/5/2022"
output: github_document
---

This file is used to read in files and write files with selected 

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(patchwork)
library(caret)
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
theme_set(theme_minimal() + theme(legend.position = "bottom") + theme(plot.title = element_text(hjust = 0.5)))
```

## Rough summary of missing Data
### M2P3
```{r}
m2p3 = read_tsv("./data/ICPSR_25281/DS0001/25281-0001-Data.tsv")

missing = m2p3 %>% 
  select_if(function(x) any(is.na(x))) %>% 
  summarise_each(funs(sum(is.na(.))))

missing %>%
  pivot_longer(M2FAMNUM:B3TEFZ2,names_to = "variables", values_to = "missing_counts") %>% 
  mutate(labels = c("Family number", "BTACT Comp Z - National", "Episodic Memory Z - National", 
                    "Exe Func Z - National", "BTACT Comp Z - Milwaukee",
                    "Episodic Memory Z - Milwaukee", "Exe Func Z - Milwaukee"),
         missing_perc = paste0(round(missing_counts/4512, 4)*100, "%")) %>% 
  select(variables, labels, everything()) %>% 
  knitr::kable(col.names = c("Variable", "Labels", "Missing Counts", "Missing Percentage"), caption = "M2 Missing Data")

```

### M3P3
```{r}
m3p3 = read.table(file = "./data/ICPSR_37095/DS0001/37095-0001-Data.tsv", sep = '\t', header = TRUE)
missing_m3p3 = 
  m3p3 %>% 
  select_if(function(x) any(is.na(x))) %>% 
  summarise_each(funs(sum(is.na(.))))
missing_m3p3 %>% 
  pivot_longer(M2FAMNUM:C3TSPXBB, names_to = "var", values_to = "missing") %>% 
  mutate(labels = c("M2 Family Number", "Backward Counting: # Correct", "Mixed-task normal nonswitch trials %correct", "Mixed-task reverse nonswitch trials %correct", "Mixed-task nonswitch trials %correct", "Mixed-task normal switch trials %correct", "Mixed-task reverse switch trials %correct", "Mixed-task switch trials %correct", "All mixed-task %correct"),
         miss_perc = paste0(round(missing/3291, 4)*100,"%")) %>% 
  select(var, labels, everything()) %>% 
  knitr::kable(col.names = c("Variable", "Labels", "Missing Counts", "Missing Percentage"), caption = "M3 Missing Data")
```


## Detailed examination 

### M2P3
Which subject? missing what. how many NA does each subject has?
```{r}
# Milwaukee sample first
#milwaukee_only = c("B3TCOMPZ2", "B3TEMZ2", "B3TEFZ2")
milwaukee_only = 
  m2p3 %>% 
  select(M2ID, B3TCOMPZ2, B3TEMZ2, B3TEFZ2) %>% 
  filter(!(is.na(B3TCOMPZ2) | is.na(B3TEMZ2) | is.na(B3TEFZ2)))
```
Milwaukee sample is, surprisingly, complete. at least in the variables for Milwaukees only. What about other variables?

```{r}
m2p3 %>% 
  filter(M2ID %in% milwaukee_only$M2ID) %>% 
  select(-c(B3TCOMPZ1, B3TEMZ1, B3TEFZ1)) %>% 
  select_if(function(x) any(is.na(x))) %>% 
  summarise_each(funs(sum(is.na(.))))
```
For Milwaukee sample only, the only missing variable is "M2FAMNUM", i.e, MIDUS 2 Family Numbers. And it seems that this variable is not collected for the Milwaukee sample at all.

Milwaukee samples have their own ID
```{r, eval = FALSE}
# national only
#national_only = c("B3TCOMPZ1", "B3TEMZ1", "B3TEFZ1")
national_only = m2p3 %>% 
  filter(!(M2ID %in% milwaukee_only$M2ID)) %>% 
  select(M2ID, B3TCOMPZ2, B3TEMZ2, B3TEFZ2) 

m2p3 %>% 
  select(M2ID, B3TCOMPZ1, B3TEMZ1, B3TEFZ1, B3TCOMPZ2, B3TEMZ2, B3TEFZ2) %>% 
  mutate(national = ifelse(is.na(B3TCOMPZ2) | is.na(B3TEMZ2) | is.na(B3TEFZ2), 1,0),
         milwaukee = ifelse(is.na(B3TCOMPZ1) | is.na(B3TEMZ1) | is.na(B3TEFZ1), 1,0)) %>% 
  filter(national==1 & milwaukee == 1)
```

```{r}
m2p3$NASUM = rowSums(is.na(m2p3))
# national sample
m2p3 %>%
  filter(!(M2ID %in% milwaukee_only$M2ID)) %>% 
  mutate(NASUM = as.integer(NASUM)) %>% 
  select(M2ID, NASUM) %>% 
  ggplot(aes(x = NASUM))+
  geom_histogram(bins = 3)+
  labs(x = "Number of NA", y = "Number of Subjects (Counts)")+
  ggtitle("Distribution of NA - M2P3 (no Milwaukee)")
```


# M3P3
```{r}
m3p3$NASUM = rowSums(is.na(m3p3))
m3p3 %>% 
  select(M2ID, NASUM) %>% 
  ggplot(aes(x = as.integer(NASUM)))+
  geom_histogram(bins = 10)+
  labs(x = "Number of NAs", y = "Number of Subjects (Counts)")+
  ggtitle("Distribution of NA - M3P3")
```


# Time gap between M2 and M3
```{r}
m2_res_time =
  m2p3 %>% 
  select(M2ID, B1PAGE_M2, B3PIDATE_MO, B3PIDATE_YR)
```
```{r}
m3_res_time = 
  m3p3 %>% 
  select(M2ID, C1PRAGE, C3IDATE_MO, C3IDATE_YR)
```
<details>
  <summary>Click to expand the data wrangling part</summary>
  
```{r}
m2_m3_time_lapse_raw = 
  left_join(m2_res_time, m3_res_time, by = "M2ID") 

m2_m3_time_lapse = 
  m2_m3_time_lapse_raw %>% 
  filter(!(is.na(C1PRAGE)|is.na(C3IDATE_MO)|is.na(C3IDATE_YR))) %>% 
  mutate(m2_date = ifelse(B3PIDATE_MO<10, paste0(B3PIDATE_YR, "0",B3PIDATE_MO), paste0(B3PIDATE_YR, B3PIDATE_MO)),
         m3_date = ifelse(C3IDATE_MO<10, paste0(C3IDATE_YR, "0",C3IDATE_MO), paste0(C3IDATE_YR, C3IDATE_MO)),
         intv_mo = interval(ym(m2_date), ym(m3_date))%/% months(1),
         intv_yr = round(interval(ym(m2_date), ym(m3_date))/ years(1),2),
         age_change = C1PRAGE - B1PAGE_M2) %>% 
  select(M2ID, m2_date, m3_date, intv_mo, intv_yr, age_change)

a = m2_m3_time_lapse_raw %>%  
  filter(is.na(C1PRAGE)|is.na(C3IDATE_MO)|is.na(C3IDATE_YR)) %>% 
  mutate(m2_date = ifelse(B3PIDATE_MO<10, paste0(B3PIDATE_YR, "0",B3PIDATE_MO), paste0(B3PIDATE_YR, B3PIDATE_MO)),
         m3_date = NA,
         intv_mo = NA,
         intv_yr = NA,
         age_change = NA) %>% 
  select(M2ID, m2_date, m3_date, intv_mo, intv_yr, age_change)
m2_m3_time_lapse = 
  rbind(m2_m3_time_lapse, a) %>% 
  arrange(M2ID)
```
</details>

Summary Statistics 
```{r}
skimr::skim(m2_m3_time_lapse[,c("M2ID", "intv_mo", "intv_yr", "age_change")])
```


Graphs
```{r}
a %>% 
  ggplot(aes(x = m2_date))+
  geom_bar() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust= 1))+
  ggtitle("Missing Subject M2 Date distribution")
den_plot = 
  m2_m3_time_lapse %>% 
  ggplot(aes(x = intv_yr))+
  geom_density()+
  ggtitle("Distirbution of Years Overlapped")
```
```{r}
box_plot = 
  m2_m3_time_lapse %>% 
  ggplot(aes(x = intv_yr))+
  geom_boxplot()
den_plot/box_plot
```

Wide distribution with a large amount of outliers, person time may be a better choice. 

Question:
invalid meaning, how to distinguish?

### Confirm milwaukee sample id

```{r}
mke1 = read_tsv("./data/MKE Data.tsv")
milwaukee_only_test = 
  inner_join(m2p3, mke1, by = "M2ID") %>% 
  select(M2ID, M2FAMNUM)
identical(milwaukee_only$M2ID, milwaukee_only_test$M2ID)
```

The filtered ID done prev to the complete dataset (M2P3) is indeed the milwaukee sample M2ID.


### Current variables extract & data preprocessing
MIDUS 2
```{r}
# prev study also in
#m2p4001:aggregated updated; m2p4002:medication stacked updated public n = 7174
m2p4 = read_tsv("./data/ICPSR_29282/DS0001/29282-0001-Data.tsv") 

m2p1 = read_tsv("./data/ICPSR_04652/DS0001/04652-0001-Data.tsv")

# no smoking yet, also included B1SA11Z (M2 - stroke history)
m2p1_selected = m2p1 %>% select(M2ID, B1PAGE_M2,  B1PRSEX, B1PF7A, B1PB1, B1PTSEI, B1PB19, B1PPARTN, B1PA6A, 
                                B1SA11W, B1SA11Z,B1SA62A, B1SA62B, B1SA62C, B1SA62D, B1SA62E, B1SA62F, 
                                B1SA62G, B1SA62H, B1SA62I, B1SA62J)
m2p4_selected = m2p4 %>% select(M2ID, B4QCT_EA, B4QCT_EN, B4QCT_MD, B4QCT_PA, B4QCT_PN, B4QCT_SA, B4HMETMW)
m2p3_selected = m2p3 %>% 
  select(M2ID, M2FAMNUM, B3TCOMPZ3, B3TEMZ3, B3TEFZ3, B3PIDATE_MO, B3PIDATE_YR)

sum(is.na(m2p3_selected$M2FAMNUM)==TRUE) # only m2p3_selected has 306 missing - family numbers
```

```{r}
# prev data integration
m2_df = list(m2p3_selected, m2p1_selected, m2p4_selected) %>% reduce(full_join, by = "M2ID") %>% 
  filter(M2ID %in% m2p3_selected$M2ID)

# Milwaukee sample family number filled in
m2_df = 
  m2_df %>% 
  mutate(M2FAMNUM = ifelse(is.na(M2FAMNUM), M2ID, M2FAMNUM))

# NA investigation
m2_df %>% 
  select_if(function(x) any(is.na(x))) %>% 
  summarise_each(funs(sum(is.na(.))))

# Most of the NA's are from M2P4. Only 1152 observations left
m2p3_selected %>% 
  filter(M2ID %in% m2p4_selected$M2ID)
```


```{r, eval = F}
m2p1_condition_nostrk = m2p1 %>% 
  select(M2ID, B1SPWBA2, B1SPWBE2, B1SPWBG2, B1SPWBR2, B1SPWBU2, B1SPWBS2, 
         B1SMASTE, B1SCONST, B1SCTRL, 
         B1SESTEE, B1SINTER, B1SINDEP,
         B1SAGENC, B1SAGREE, B1SNEURO, B1SCONS1)  # no b1sexta, find it in the code book
```

MIDUS 3
```{r}
m3p1 = read_tsv("./data/ICPSR_36346/DS0001/36346-0001-Data.tsv")
m3p1_selected = m3p1 %>% 
  select(M2ID, C1PA6A, C1SA11Z, C1PB19)

m3p3_selected = m3p3 %>% 
  select(M2ID, M2FAMNUM, C3TCOMP, C3TEM, C3TEF, C3IDATE_MO, C3IDATE_YR, C1PRAGE)

sum(is.na(m3p3_selected$C1PRAGE)==TRUE) #family number missing
```

```{r}
m3_df = list(m3p3_selected, m3p1_selected) %>% reduce(left_join, by = "M2ID")

# 
m3_df %>% 
  filter(M2ID %in% m2_df$M2ID) %>% 
  filter(is.na(M2ID))

m3_df %>% 
  filter(is.na(M2FAMNUM)) %>%  # left join: 330 missing the family num, need the m3 mke
  filter(!(M2ID %in% milwaukee_only_test$M2ID))

# for now, just fill in their M2ID as family numbers
m3_df =  m3_df %>% 
  mutate(M2FAMNUM = ifelse(is.na(M2FAMNUM), M2ID, M2FAMNUM))
```


### Stroke analysis
```{r}
# missing: or: 1670, and: 1670
# 0:no, 1:yes, 7:dk
stroke_df = merge(x = m2p1_selected[, c("M2ID", "B1PA6A", "B1SA11Z")], y = m3p1_selected[,c("M2ID", "C1PA6A", "C1SA11Z")], by = "M2ID", all.x=TRUE) %>%
  filter(!(is.na(C1PA6A) & is.na(C1SA11Z))) %>% 
  mutate(B1PA6A = recode(B1PA6A, `2` = 0),
         C1PA6A = recode(C1PA6A, `2` = 0),
         B1SA11Z = recode(B1SA11Z, `2` = 0),
         C1SA11Z = recode(C1SA11Z, `2` = 0),
         D1PA6A = C1PA6A - B1PA6A, # D for delta
         D1SA11Z = C1SA11Z - B1SA11Z)  
# stroke history var does not contain refused
# Stroke history: the unchanged
stroke_df %>% 
  filter(D1PA6A == 0) %>% 
  group_by(B1PA6A, C1PA6A) %>% 
  summarize(n = n())

# History: the changed: 0->1(1 target), 1->0(-1 invalid), 0->7(7 dk), 7->0(-7 invalid?), 7->1(-6 target), 1->7(6 invalid)
stroke_df %>% 
  filter(D1PA6A != 0) %>% 
  group_by(D1PA6A) %>% 
  summarize(n = n())

# within 12 month contains refused and missing, filtered out during data processing
# stroke within 12 months, unchanged (1->1, reoccurring strokes?)
stroke_df %>% 
  filter(!(B1SA11Z %in% c(-1,8) | C1SA11Z %in% c(-1,8))) %>% 
  filter(D1SA11Z == 0) %>% 
  select(-c(B1PA6A, C1PA6A, D1PA6A)) %>% 
  group_by(B1SA11Z, C1SA11Z) %>% 
  summarize(n = n())

# stroke within 12 months, changed
stroke_df %>% 
  filter(!(B1SA11Z %in% c(-1,8) | C1SA11Z %in% c(-1,8))) %>% 
  filter(D1SA11Z != 0) %>% 
  select(-c(B1PA6A, C1PA6A, D1PA6A)) %>% 
  group_by(B1SA11Z, C1SA11Z,D1SA11Z) %>% 
  summarize(n = n())

# inconsistency: history and recent 12 month (?)
# those who report having strokes recently but report no stroke history


```

### Marital status change 
```{r}
# combine data, right now just focus on the non-missing subjects
mar_df = merge(x = m2p1_selected[, c("M2ID", "B1PB19")], 
               y = m3p1_selected[,c("M2ID", "C1PB19")], by = "M2ID", all.x=TRUE) %>% 
  drop_na()

# the results are quite spreaded-out, how to code for them?
mar_df %>% 
  mutate(D1PB19 = C1PB19 - B1PB19) %>% 
  filter(D1PB19 != 0) %>% 
  group_by(B1PB19, C1PB19, D1PB19) %>% 
  summarize(n = n())
```



### Univariate Analysis
thoughts on univariate analysis rn: level and change in EF and EM. 

Very primitive, need to change later
```{r}
# parameters setup 
theme1 = trellis.par.get()
theme1$plot.symbol$col = rgb(0.4556, 0.5444, 0, .3) #
theme1$plot.symbol$pch = 16
theme1$plot.line$col = rgb(0.8, 0, 0.2, 1) #0.5316, 0.4684
theme1$plot.line$lwd = 2
theme1$strip.background$col = rgb(0.2611, 0.2124, 0.5265, .2)
trellis.par.set(theme1)
```

```{r fig.height=10, fig.width=10, out.width="90%"}
# M2 continuous
m2_df_graph_cont = m2_df %>% 
  drop_na() %>% 
  select(-c(B1PRSEX, B1PF7A, B1PB19, B1PPARTN, B1PA6A, B1SA11W, B1SA11Z, B1SA62A, B1SA62B, 
            B1SA62C, B1SA62D, B1SA62E, B1SA62F, B1SA62G, B1SA62H, B1SA62I, B1SA62J, B3PIDATE_MO, B3PIDATE_YR)) %>% 
  filter(B4QCT_SA <= 25 & B1PTSEI <= 80.53 & B4HMETMW <= 26355 & B4QCT_EN <=25 & B4QCT_MD <= 3 & B4QCT_PN <= 21 &
           B1PB1 <= 12 & B4QCT_EA <= 25 & B3TCOMPZ3 < 4 & B3TEMZ3 < 4 & B3TEFZ3 < 4)

# Cognition composite score
x_feature = model.matrix(`B3TCOMPZ3` ~., m2_df_graph_cont[3:15])[, -1]
y = m2_df_graph_cont$B3TCOMPZ3
featurePlot(x_feature, y, plot = "scatter", labels = c("", "Composite Scores"),
            type = c("p", "smooth"), layout = c(3,4))

# Episodic Memory
x_feature = model.matrix(`B3TEMZ3` ~., m2_df_graph_cont[3:15])[, -1]
y = m2_df_graph_cont$B3TEMZ3
featurePlot(x_feature, y, plot = "scatter", labels = c("", "Episodic Memory"),
            type = c("p", "smooth"), layout = c(3,4))

# Executive Function
x_feature = model.matrix(`B3TEFZ3` ~., m2_df_graph_cont[3:15])[, -1]
y = m2_df_graph_cont$B3TEFZ3
featurePlot(x_feature, y, plot = "scatter", labels = c("", "Executive Function"),
            type = c("p", "smooth"), layout = c(3,4))

```
```{r fig.height=10, fig.width=10, out.width="90%"}
m2_df_graph_cate = m2_df %>% 
  drop_na() %>% 
  select(c(B3TCOMPZ3, B3TEMZ3, B3TEFZ3, B1PRSEX, B1PF7A, B1PB19, B1PPARTN, B1PA6A, B1SA11W, B1SA11Z, B1SA62A, B1SA62B, 
            B1SA62C, B1SA62D, B1SA62E, B1SA62F, B1SA62G, B1SA62H, B1SA62I, B1SA62J))
```




### TODO: missing value investigation (look at dataset other than the aggregated one, etc.), milwaukee sample data integration, add smoking var | family number (random intercept for each family - LMM), 

