---
title: "Updates"
author: "Paula Wu"
date: "4/20/2022"
output: github_document
---

### Apr.20 Updates
1. Get rid of the outliers in `B3TCOMPZ3`,`B3TEMZ3`, `B3TEFZ3` and re-draw the graphs. 
2. M3 family number investigation and imputation. Integrate the milwaukee sample data to the working datasets. 
3. For M2, only focus on subjects that has CTQ numbers. Integrate the milwaukee sample data to the working datasets. 
4. Recode for marital status (1 - married; 0 - other status)
5. Correlation Plot

### TODO
1. Stroke: report inconsistency
2. Covariates investigations
3. Resilience Factor
4. Missing Data proportion
5. Smoking
6. Modeling

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(patchwork)
library(caret)
library(GGally)
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
theme_set(theme_minimal() + theme(legend.position = "bottom") + theme(plot.title = element_text(hjust = 0.5)))
```

```{r, echo=FALSE}
# reading datas
m2p3 = read_tsv("./data/ICPSR_25281/DS0001/25281-0001-Data.tsv")
m3p3 = read.table(file = "./data/ICPSR_37095/DS0001/37095-0001-Data.tsv", sep = '\t', header = TRUE)
mke1 = read_tsv("./data/MKE Data.tsv")
m2p4 = read_tsv("./data/ICPSR_29282/DS0001/29282-0001-Data.tsv") 
m2p1 = read_tsv("./data/ICPSR_04652/DS0001/04652-0001-Data.tsv")
m3p1 = read_tsv("./data/ICPSR_36346/DS0001/36346-0001-Data.tsv")
mke2 = read_tsv("./data/ICPSR_37120/DS0001/37120-0001-Data-REST.tsv")
```

```{r, echo=FALSE}
# no smoking yet, also included B1SA11Z (M2 - stroke history)
m2p1_selected = m2p1 %>% 
  select(M2ID, B1PAGE_M2,  B1PRSEX, B1PF7A, B1PB1, B1PTSEI, B1PB19, B1PPARTN, B1PA6A, 
         B1SA11W, B1SA11Z,B1SA62A, B1SA62B, B1SA62C, B1SA62D, B1SA62E, B1SA62F, 
         B1SA62G, B1SA62H, B1SA62I, B1SA62J)
m2p4_selected = m2p4 %>% 
  select(M2ID, B4QCT_EA, B4QCT_EN, B4QCT_MD, B4QCT_PA, B4QCT_PN, B4QCT_SA, B4HMETMW)
m2p3_selected = m2p3 %>% 
  select(M2ID, M2FAMNUM, B3TCOMPZ3, B3TEMZ3, B3TEFZ3, B3PIDATE_MO, B3PIDATE_YR)
m3p1_selected = m3p1 %>% 
  select(M2ID, C1PA6A, C1SA11Z, C1PB19)
m3p3_selected = m3p3 %>% 
  select(M2ID, M2FAMNUM, C3TCOMP, C3TEM, C3TEF, C3IDATE_MO, C3IDATE_YR, C1PRAGE)
```

## MIDUS 2
```{r}
# Data integration
m2_df = list(m2p3_selected, m2p1_selected, m2p4_selected) %>% reduce(full_join, by = "M2ID")

# Milwaukee sample family number filled in
m2_df = 
  m2_df %>% 
  mutate(M2FAMNUM = ifelse(is.na(M2FAMNUM), M2ID, M2FAMNUM))

# only keep those with CTQ numbers
m2_df = 
  m2_df %>% 
  filter(!(is.na(B4QCT_EA) & is.na(B4QCT_EN) & is.na(B4QCT_MD) & is.na(B4QCT_PA) & is.na(B4QCT_PN) & is.na(B4QCT_SA)))

# milwaukee sample information filled in
mke1_in_m2= intersect(m2_df$M2ID, mke1$M2ID)

# ethnicity: BACR7A = 2
# don't have cohabitation in mke1, impute as NA
mke1_to_add = 
  mke1 %>% 
  select(M2ID, BACRAGE, BACRSEX, BACB1, BACTSEI, BACB19, BACA6A, BACAS11W, BACAS11Z, 
         BACAS62A, BACAS62B, BACAS62C, BACAS62D, BACAS62E, BACAS62F, BACAS62G, BACAS62H, BACAS62I, BACAS62J) %>% 
  filter(M2ID %in% mke1_in_m2) %>% 
  mutate(BACR7A = 2, BACPARTN = NA) %>%  # added two more columns
  select(M2ID, BACRAGE, BACRSEX, BACR7A, BACB1, BACTSEI, BACB19, BACPARTN, everything())

# fill in data
for (i in 1:(length(mke1_to_add)-1)){
  for (j in mke1_to_add$M2ID){
    m2_df[m2_df$M2ID == j, i+7] = mke1_to_add[mke1_to_add$M2ID == j, i+1]
  }
}

# Marital Status recoding (1-married; 0-others)
m2_df =
  m2_df %>% 
  mutate(B1PB19 = ifelse(B1PB19 == 1, 1, 0))
```

Done MIDUS 2 dataset integrations and imputations


## MIDUS 3
```{r}
m3_df = list(m3p3_selected, m3p1_selected) %>% reduce(left_join, by = "M2ID")

mke2_in_m3= intersect(m3_df$M2ID, mke2$M2ID)
```

All subjects whose don't have family numbers are from the Milwaukee sample (MKE2). Impute with their own ID.

```{r}
m3_df = 
  m3_df %>% 
  mutate(M2FAMNUM = ifelse(is.na(M2FAMNUM), M2ID, M2FAMNUM))
```

```{r}
# data imputation 
mke2_to_add = 
  mke2 %>% 
  select(M2ID, CACA6A, CACAS11Z, CACB19)

for (i in 1:(length(mke2_to_add)-1)){
  for (j in mke2_to_add$M2ID){
    m3_df[m3_df$M2ID == j, i+8] = mke2_to_add[mke2_to_add$M2ID == j, i+1]
  }
}
```


### Univariate Analysis
```{r}
# parameters setup 
theme1 = trellis.par.get()
theme1$plot.symbol$col = rgb(0.4556, 0.5444, 0, .3) #
theme1$plot.symbol$pch = 16
theme1$plot.line$col = rgb(0.8, 0, 0.2, 1) #0.5316, 0.4684
theme1$plot.line$lwd = 2
theme1$strip.background$col = rgb(0.2611, 0.2124, 0.5265, .2)
trellis.par.set(theme1)
```

```{r fig.height=10, fig.width=10, out.width="90%"}
# M2 continuous
m2_df_graph_cont = m2_df %>% 
  select(-c(B1PRSEX, B1PF7A, B1PB19, B1PPARTN, B1PA6A, B1SA11W, B1SA11Z, B1SA62A, B1SA62B, 
            B1SA62C, B1SA62D, B1SA62E, B1SA62F, B1SA62G, B1SA62H, B1SA62I, B1SA62J, B3PIDATE_MO, B3PIDATE_YR)) %>% 
  filter(B4QCT_SA <= 25 & B1PTSEI <= 80.53 & B4HMETMW <= 26355 & B4QCT_EN <=25 & B4QCT_MD <= 3 & B4QCT_PN <= 21 &
           B1PB1 <= 12 & B4QCT_EA <= 25 & B3TCOMPZ3 < 4 & B3TEMZ3 < 4 & B3TEFZ3 < 4)

# Cognition composite score
x_feature = model.matrix(`B3TCOMPZ3` ~., m2_df_graph_cont[3:15])[, -1]
y = m2_df_graph_cont$B3TCOMPZ3
featurePlot(x_feature, y, plot = "scatter", labels = c("", "Composite Scores"),
            type = c("p", "smooth"), layout = c(3,4))

# Episodic Memory
x_feature = model.matrix(`B3TEMZ3` ~., m2_df_graph_cont[3:15])[, -1]
y = m2_df_graph_cont$B3TEMZ3
featurePlot(x_feature, y, plot = "scatter", labels = c("", "Episodic Memory"),
            type = c("p", "smooth"), layout = c(3,4))

# Executive Function
x_feature = model.matrix(`B3TEFZ3` ~., m2_df_graph_cont[3:15])[, -1]
y = m2_df_graph_cont$B3TEFZ3
featurePlot(x_feature, y, plot = "scatter", labels = c("", "Executive Function"),
            type = c("p", "smooth"), layout = c(3,4))
```

Correlation Plot of independent variables in M2 dataset (i.e. `B3TCOMPZ3`,`B3TEMZ3`, `B3TEFZ3` are not included in the graph)
```{r fig.height=10, fig.width=10, out.width="100%"}
m2_df %>% 
  select(-c(M2ID, M2FAMNUM, B3TCOMPZ3, B3TEMZ3, B3TEFZ3)) %>% 
  ggcorr(label=TRUE, hjust = 0.9, layout.exp = 2, label_size = 3, label_round = 2)
  #ggtitle("After") +
  #theme(plot.title = element_text(hjust = 0.5)) +
  #labs(caption = "1.b")
```

High correlation between marital status and cohabitation, among the drug use variables (`B1SA62A - J`), among the CTQ score variables (`B4QCT_EA`, `B4QCT_EN`, `B4QCT_MD`, `B4QCT_PA`, `B4QCT_PN`, `B4QCT_SA`).
